---
title: "Rworksheet_delfin#2"
author: "Shaun Angelo Delfin"
date: "2024-09-25"
output: html_document

# 1. Create a vector using : operator
```{r}
# a. Sequence from -5 to 5. Write the R code and its output. Describe its output.
sequence. <- -5:5
print (sequence)

#the output of this code is from negative five to positive five.

# b. x <- 1:7. What will be the value of x?
x <- 1:7
print(x)
#The value of x are numbers from one to seven.
```
2. Create a vector using seq() function
a. seq(1, 3, by=0.2) # specify step size
Write the R script and its output
```{r}
num <- seq(1,3, by = 0.2)
print(num)
```
Describe the output
- The output is sequenced vector that starts with 1 until 3

 # 3. A factory has a census of its workers. There are 50 workers in total. The following list shows their ages:
```{r}
ages <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29, 35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 43, 53, 41, 51, 35, 24,33, 41, 53, 40, 18, 44, 38, 41, 48, 27, 39, 19, 30, 61, 54, 58, 26, 18)

```
a. Access 3rd element, what is the value?
```{r}
third <- ages[c(2,4)]
print(third)
```
b. Access 2nd and 4th element, what are the value?
```{r}
sec_fourth <- ages[c(2,4)]
print(sec_fourth)
```
c. Access all but the 4th and 12th element is not included. Write the R script and its output.
```{r}
all <- ages[-c(4,12)]
print(x)
```

4. Create a vector x <- c("first"=3 "second"=0, "third"=9). then named the
vector, names(x)
```{r}
x <- c("first" = 3, "second" = 0, "third" = 9)
print(x)
```
a. Print the results. Then access x[c("first", "third")].
```{r}
names <- x[c("first", "third")]
print(names)
```
Describe the output

-The output is showing 3 vectors and then accessing elements of the first and third by giving names.

5. Create a sequence x from -3:2.
a. Modify 2nd element and change it to 0;
x[2] <- 0
x
```{r}


```

```





