---
title: "Rworksheet_Delfin#1"
output: pdf_document
date: "2024-09-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. Age Vector

```{r}
age <- c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41.)
length(age)
```
a. Data points
b.R code output

2. Reciprocal Age
```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,
35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,
51, 35, 24, 33, 41.)
reciprocalage <- 1/age
print(reciprocalage)
```
3. Assign new age
```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,51, 35, 24, 33, 41.)
newage <-c (age, 0, age)
print (newage)
```
4. Sort Values
```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41,51, 35, 24, 33, 41.)
sort_age <- sort(age)
print(sort_age)
```
5. Find Minimum and Maximum
```{r}
age <-c(34, 28, 22, 36, 27, 18, 52, 39, 42, 29,35, 31, 27, 22, 37, 34, 19, 20, 57, 49, 50, 37, 46, 25, 17, 37, 42, 53, 41, 51, 35, 24, 33, 41.)
minage <-(age)
maxage <-(age)
print(minage)
print(maxage)
```
6. 2nd Data set
```{r}
data <-c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
length(data)
```
7. Doubled data
```{r}
data <- c(2.4, 2.8, 2.1, 2.5, 2.4, 2.2, 2.5,
2.3, 2.5, 2.3, 2.4, 2.7)
datadoubled <-  data_*2
print(datadoubled)
```
8. Sequence
+8.1
```{r}
seq(1:100)
```
+8.2
```{r}
seq(20:60)
```
+8.3
```{r}
mean(20:60)
```
8.4
```{r}
sum(51:91)
```
8.5
```{r}
seq(1:1000)
```
9. Filter
```{r}
Filter(funvtion(i) { all(i %% c(3,5,7) !=0) }, seq(100))
```
10.Backward
```{r}
```

11. 11. List all the natural numbers below 25 that are multiples of 3 or 5.
Find the sum of these multiples.

a. How many data points from 10 to 11?

 3 + 5 + 6 + 9 + 10 + 12 + 15 + 18 + 20 + 21 + 24 = 143.

b. Write the R code and its output from 10 and 11.

```{r}
multiples <- c(3, 5, 6, 9, 10, 12, 15, 18, 20, 21, 24)
sum_multiples <- sum(multiples)
print(paste("Sum of multiples:", sum_multiples))
seq1 <- 10:11
```

12. Statements can be grouped together using braces ‘{’ and ‘}’. A group of statements
is sometimes called a block. Single statements are evaluated when a new line is typed
at the end of the syntactically complete statement. Blocks are not evaluated until a
new line is entered after the closing brace.
Enter this statement:

x <- {0 + x + 5 + }

Describe the output.

13. *Set up a vector named score, consisting of 72, 86, 92, 63, 88, 89, 91, 92, 75,
75 and 77. To access individual elements of an atomic vector, one generally uses the
x[i] construction.
```{r}
score <- c(72, 86, 92, 63, 88, 89, 91, 92, 75, 75, 77)
```

Find x[2] and x[3]. Write the R code and its output.
```{r}
x2 <- score[2]
x3 <- score[3]
print(paste("x[2] =", x2))
print(paste("x[3] =", x3))
```

14. *Create a vector a = c(1,2,NA,4,NA,6,7).
a. Change the NA to 999 using the codes print(a,na.print="-999").
```{r}
{r}
a <- c(1, 2, NA, 4, NA, 6, 7)
print(a)
print(a, na.print="-999")
```


15. A special type of function calls can appear on the left hand side of the assignment
operator as in > class(x) <- "foo".
Follow the codes below:
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
What is the output of the above code?
```{r}
name = readline(prompt="Input your name: ")
age = readline(prompt="Input your age: ")
print(paste("My name is",name, "and I am",age ,"years old."))
print(R.version.string)
```